---
title: "RSV"
format: pdf
---

# Training Data Format

| Field | Description | Default or source |
|----------------|--------------------------|------------------------------|
| `location_code` | Location identifier | `influpaint/influpaint_locations.csv` |
| `value` | Observed/modelled values | All rates or all counts, scaled consistently |
| `fluseason_week` | Week index within season | `season_week()` 1 to 53 |
| `fluseason` | Season start year | `season_year()` |
| `datasetH1` | High level dataset identifier | e.g. RSV scenario modelling hub |
| `datasetH2` | Specific dataset or scenario identifier | e.g. 2023-11-12-NIH-RSV_Phenomenological |
| `sample` | Sample identifier | e.g. 1.1, 1.2 |

```{r, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 7,
  dpi = 300
)
```

# Helpers

```{r, helpers}
library(tidyverse)
library(arrow)

location_codes <- read_csv("influpaint/influpaint_locations.csv")

#' Get the season year for a given date
#' @param date A Date object
#' @param start_month Integer. Month defining season start. Default is June.
#' @return Integer. The season year.
#' @details
#' The start of the season is defined by `start_month` (default is June).
#' If the date is on or after `start_month`, the season year is the current year.
#' Else, it is the previous year.
season_year <- function(date, start_month = 6) {
  year <- as.integer(format(date, "%Y"))
  month <- as.integer(format(date, "%m"))
  ifelse(month >= start_month, year, year - 1)
}
#' Get the week index within the season for a given date
#' @param date A Date object
#' @param start_month Integer. Month defining season start. Default is June.
#' @return Integer. Week index within the season (1 to 53)
#' @details
#' The start of the season is defined by `start_month` (default is June).
#' The week index is calculated as the number of weeks since the season start date.
season_week <- function(date, start_month = 6) {
  sy <- season_year(date, start_month)
  season_start <- as.Date(paste(sy, start_month, 1, sep = "-"))
  as.integer(floor(as.numeric(date - season_start) / 7) + 1)
}
```

# Gather RSV Data

## NSSP

National Syndromic Surveillance Program Emergency Department Visits [source](https://cmu-delphi.github.io/delphi-epidata/api/covidcast-signals/nssp.html)

**`pct_ed_visits_rsv` : Percent of ED visits that had a discharge diagnosis code of rsv**

*Earliest date available: 2022-10-01*

```{r, nssp}
library(epidatr)
nssp <- pub_covidcast(
  source = "nssp",
  signals = "pct_ed_visits_rsv",
  geo_type = "state",
  time_type = "week"
) |>
  mutate(geo_value = str_to_upper(geo_value)) |>
  left_join(
    location_codes |>
      select(abbreviation, location_code),
    by = c("geo_value" = "abbreviation")
  ) |>
  transmute(
    location_code,
    fluseason = season_year(as.Date(time_value)),
    fluseason_week = season_week(as.Date(time_value)),
    value,
    datasetH1 = "NSSP",
    datasetH2 = "NSSP",
    sample = "1"
  )

nssp |>
  ggplot(aes(x = fluseason_week, y = location_code)) +
  facet_wrap(~fluseason) +
  geom_tile(aes(fill = value)) +
  scale_fill_viridis_c() +
  scale_x_continuous(breaks = seq(1, 53, by = 4)) +
  theme_classic()

nssp |>
  skimr::skim() |>
  as_tibble() |>
  select(skim_variable, complete_rate)
write_parquet(nssp, "RSV_files/NSSP.parquet")
```

## RSV-Net

Weekly Rates of Laboratory-Confirmed RSV Hospitalizations from the RSV-NET Surveillance System [source:](https://data.cdc.gov/Public-Health-Surveillance/Weekly-Rates-of-Laboratory-Confirmed-RSV-Hospitali/29hc-w46k/about_data)

RSV scenario modeling hub [time-series.csv](https://github.com/midas-network/rsv-scenario-modeling-hub/tree/main/target-data) converts to **weekly number of hospitalizations in each given state**

```{r, rsvnet}
rsvnet <- read_csv(
  "https://raw.githubusercontent.com/midas-network/rsv-scenario-modeling-hub/main/target-data/time-series.csv"
) |>
  filter(
    age_group == "0-130",
    location != "US"
  ) |>
  transmute(
    location_code = location,
    fluseason = season_year(date),
    fluseason_week = season_week(date),
    value = observation,
    datasetH1 = "RSV-Net",
    datasetH2 = "RSV-Net",
    sample = "1"
  ) |>
  filter(fluseason >= 2018)

rsvnet |>
  ggplot(aes(x = fluseason_week, y = location_code)) +
  facet_wrap(~fluseason) +
  geom_tile(aes(fill = value)) +
  scale_fill_viridis_c() +
  scale_x_continuous(breaks = seq(1, 53, by = 4)) +

  theme_classic()

rsvnet |>
  skimr::skim() |>
  as_tibble() |>
  select(skim_variable, complete_rate)
write_parquet(rsvnet, "RSV_files/RSV_NET.parquet")
```

Missing values & exlcude 2020?

## NHSN
National Healthcare Safety Network (NHSN) [source](https://data.cdc.gov/Public-Health-Surveillance/Weekly-Hospital-Respiratory-Data-HRD-Metrics-by-Ju/ua7e-t2fy/about_data)

**`totalconfrsvnewadm`: Total number of new hospital admissions of patients with confirmed RSV captured during the reporting week (Sunday - Saturday)**

```{r, nhsn}
library(RSocrata)

nhsn <- read.socrata("https://data.cdc.gov/resource/ua7e-t2fy.json") |>
  select(
    weekendingdate,
    jurisdiction,
    totalconfrsvnewadm
  ) |>
  transmute(
    fluseason = season_year(as.Date(weekendingdate)),
    fluseason_week = season_week(as.Date(weekendingdate)),
    abbreviation = jurisdiction,
    value = as.numeric(totalconfrsvnewadm),
    datasetH1 = "NHSN",
    datasetH2 = "NHSN",
    sample = "1"
  ) |>
  filter(abbreviation != "USA") |>
  left_join(
    location_codes |> select(abbreviation, location_code),
    by = "abbreviation"
  ) |>
  drop_na(location_code) |>
  filter(fluseason >= 2023)

nhsn |>
  ggplot(aes(x = fluseason_week, y = location_code)) +
  facet_wrap(~fluseason) +
  geom_tile(aes(fill = value)) +
  scale_fill_viridis_c() +
  scale_x_continuous(breaks = seq(1, 53, by = 4)) +
  theme_classic()


nhsn |>
  skimr::skim() |>
  as_tibble() |>
  select(skim_variable, complete_rate)

write_parquet(nhsn, "RSV_files/NHSN.parquet")
```

## Modelling Hub

Sample output: Each trajectory must have a unique identifier combining `run_grouping` and `stochastic_run`. Quantile and CDF outputs: There is no stochastic variation. The sample column can also be set to `NA` or to a consistent identifier that reflects the quantile or epiweek?

```{r, rsv_smh}
library(httr2)
library(purrr)

gh_ls <- function(url) {
  request(url) |> req_perform() |> resp_body_json()
}

base <- "https://api.github.com/repos/midas-network/rsv-scenario-modeling-hub/contents/model-output"

parquet_files <-
  gh_ls(base) |>
  keep(~ .x$type == "dir") |>
  map(~ gh_ls(.x$url)) |>
  flatten() |>
  keep(~ grepl("\\.parquet$", .x$name))

data <- parquet_files |>
  set_names(map_chr(
    parquet_files,
    ~ sub(".*/(.*)\\.gz\\.parquet$", "\\1", .x$path)
  )) |>
  map(~ read_parquet(.x$download_url))

library(tidytable)
rsv_smh <- data |>
  imap(
    ~ .x |>
      as_tidytable() |>
      filter(
        target == "inc hosp",
        age_group == "0-130"
      ) |>
      mutate(
        forecast_date = as.Date(origin_date) + weeks(horizon - 1),
        run_grouping = if ("run_grouping" %in% names(.)) {
          run_grouping
        } else {
          NA_character_
        },
        stochastic_run = if ("stochastic_run" %in% names(.)) {
          stochastic_run
        } else {
          NA_character_
        },
      ) |>
      transmute(
        location_code = location,
        fluseason = season_year(forecast_date),
        fluseason_week = season_week(forecast_date),
        value,
        datasetH1 = "RSV_SMH",
        datasetH2 = paste(.y, scenario_id, sep = "_"),
        sample = case_when(
          output_type == "sample" ~ paste0(run_grouping, "_", stochastic_run),
          output_type == "quantile" ~ paste0("q", output_type_id),
          output_type == "cdf" ~ paste0("p", output_type_id)
        )
      )
  ) |>
  bind_rows() |>
  filter(location_code != "US")

# --------- Sanity ---------
# Keep only fluseasons matching the first season per datasetH2
rsv_smh <- rsv_smh |>
  group_by(datasetH2) |>
  filter(fluseason == min(fluseason)) |>
  ungroup()

# Aggregated plot
plot_data <- rsv_smh |>
  summarise(
    value = mean(value, na.rm = TRUE),
    .by = c(fluseason, datasetH2, location_code, fluseason_week)
  )
plot_data |>
  filter(fluseason == "2024") |>
  ggplot(aes(x = fluseason_week, y = location_code)) +
  facet_wrap(~datasetH2) +
  geom_tile(aes(fill = value)) +
  scale_fill_viridis_c() +
  scale_x_continuous(breaks = seq(1, 53, by = 4)) +
  theme_classic()

write_parquet(rsv_smh, "RSV_files/RSV_SMH.parquet")
```


## Converting NSSP to Counts
We converted NSSP data, which records the percentage of emergency department visits due to RSV, into estimated admission counts. Using weeks and locations with NHSN data (which records the counts), we learned a location-specific scaling factor linking the reported percentage to actual counts. The scaling was done using a Poisson generalized linear mixed-effects model (GLMM) with a random intercept for each location. The predicted counts are the observed percentage scaled by the learned location-specific factor.

```{r, nssp_counts}
library(lme4)

# Predict counts and merge
nssp <- read_parquet("RSV_files/NSSP.parquet")
nhsn <- read_parquet("RSV_files/NHSN.parquet")


fit_glmm <- inner_join(
  nssp |>
    select(location_code, fluseason, fluseason_week, value),
  nhsn |>
    select(location_code, fluseason, fluseason_week, value),
  by = c("location_code", "fluseason", "fluseason_week")
) |>
  filter(value.y >= 0, value.x > 0) |>
  mutate(log_value = log(value.x)) |>
  (\(x) {
    glmer(
      value.y ~ (1 | location_code) + offset(log_value),
      data = x,
      family = poisson(link = "log")
    )
  })()

nssp_counts <- nssp |>
  filter(value > 0) |>
  mutate(
    log_value = log(value),
    value = predict(fit_glmm, newdata = cur_data(), type = "response")
  ) |>
  select(location_code, fluseason, fluseason_week, value) |>
  right_join(
    nssp |> select(-value),
    by = c("location_code", "fluseason", "fluseason_week")
  )

write_parquet(nssp_counts, "RSV_files/NSSP_COUNTS.parquet")

#NHSN vs NSSP Plot
bind_rows(
  nssp_counts |> mutate(source = "NSSP (Estimated)"),
  nhsn |> mutate(source = "NHSN (Actual)")
) |>
  ggplot(aes(
    x = fluseason_week,
    y = value,
    colour = location_code,
    linetype = source
  )) +
  facet_wrap(~ fluseason + source) +
  geom_line(alpha = 0.8) +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(1, 53, by = 7))

```

# Summary

Surveillance data includes:
- NSSP: Estimated ED visits due to RSV (converted to counts) -> `{r} nrow(nssp_counts)` rows.\
- RSV-Net: Laboratory-confirmed RSV hospitalizations -> `{r} nrow(rsvnet)` rows.\
- NHSN: Hospital admissions of patients with confirmed RSV -> `{r} nrow(nhsn)` rows.\

Modeling data includes:
- RSV Scenario Modeling Hub: Projected hospitalizations under various scenarios -> `{r} nrow(rsv_smh)` rows.\ 
However we will only take 20 samples per model and scenario for training.

- 2025 is dropped.

```{r, all_data}
set.seed(123)
rsv_smh20 <- read_parquet("RSV_files/RSV_SMH.parquet") |>
  group_by(datasetH2) |>
  filter(sample %in% sample(unique(sample), min(length(unique(sample)), 20))) |>
  ungroup()


rsv_all <- bind_rows(
  read_parquet("RSV_files/NSSP_COUNTS.parquet"),
  read_parquet("RSV_files/RSV_NET.parquet"),
  read_parquet("RSV_files/NHSN.parquet"),
  rsv_smh20
) |>
  #drop 2025
  filter(fluseason < 2025)

write_parquet(rsv_all, "RSV_files/RSV_ALL.parquet")
```


# Filling Missing RSV_SMH Values
This code fills missing values in the RSV_SMH dataset, which may occur because SMH started modelling late in the season. For each location and week, it first uses the NHSN value from the same season if available. If not, it randomly samples from NHSN values for that location and week across all seasons (the latter may be unreasonable)...

```{r}
set.seed(1)

nhsn_pool <- rsv_all |>
  filter(datasetH1 == "NHSN", !is.na(value)) |>
  group_by(location_code, fluseason_week) |>
  summarise(
    value_pool = list(value),
    .groups = "drop"
  )

nhsn_same_year <- rsv_all |>
  filter(datasetH1 == "NHSN") |>
  select(
    location_code,
    fluseason_week,
    fluseason,
    nhsn_year_value = value
  )


safe_sample <- function(x) {
  if (is.null(x) || length(x) == 0 || all(is.na(x))) {
    NA_real_
  } else {
    sample(x, 1)
  }
}

rsv_filled <- rsv_all |>
  left_join(
    nhsn_same_year,
    by = c("location_code", "fluseason_week", "fluseason")
  ) |>
  left_join(
    nhsn_pool,
    by = c("location_code", "fluseason_week")
  ) |>
  mutate(
    nhsn_draw = vapply(value_pool, safe_sample, numeric(1)),
    value = case_when(
      datasetH1 != "RSV_SMH" ~ value,
      !is.na(value) ~ value,
      !is.na(nhsn_year_value) ~ nhsn_year_value,
      TRUE ~ nhsn_draw
    )
  ) |>
  select(-nhsn_year_value, -value_pool, -nhsn_draw)


write_parquet(rsv_filled, "RSV_files/RSV_FILLED.parquet")
```


# Sanity Checks
1- Check that RSV SMH datasetH2 has unique fluseasons
```{r, sanity}
set.seed(123)
rsv_smh <- read_parquet("RSV_files/RSV_SMH.parquet")
# check that there is a unique fluseason per datasetH2
rsv_smh |>
  group_by(datasetH2) |>
  summarise(n_fluseason = n_distinct(fluseason)) |>
  filter(n_fluseason > 1)
```


# Build RSV Training Data
```{python}
import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
from pathlib import Path
import xarray as xr
import datetime
# InfluPaint modular imports
from influpaint.utils import SeasonAxis
from influpaint.utils import plotting as idplots
from influpaint.utils import converters
from influpaint.datasets import mixer as dataset_mixer
# Setup
season_setup = SeasonAxis.for_flusight(remove_us=True, remove_territories=True)
today = datetime.datetime.now().strftime("%Y-%m-%d")
Path("training_datasets").mkdir(parents=True, exist_ok=True)
```


# Helpers
`build_dataset_from_framelist` function to convert list of dataframes to xarray DataArray
```{python}
def build_dataset_from_framelist(frame_list):
    main_origins = []
    for i, frame in enumerate(frame_list):
        df = frame_list[i]
        df["fluseason"] = i
        frame_list[i] = df
        assert df.season_week.max() == 53 and df.season_week.min() == 1
        
        main_origins.append(df["origin"].mode()[0] if not df["origin"].mode().empty else None)
        
    all_frames_df = pd.concat(frame_list).reset_index(drop=True)
    array_list = converters.dataframe_to_arraylist(df=all_frames_df, season_setup=season_setup)
    array = np.array(array_list)
    flu_payload_array = xr.DataArray(array, 
                    coords={'sample': np.arange(array.shape[0]),
                        'feature': np.arange(array.shape[1]),
                        'season_week': np.arange(1, array.shape[2]+1),
                        'place': season_setup.locations + [""]*(array.shape[3] - len(season_setup.locations))}, 
                    dims=["sample", "feature", "season_week", "place"])
    return flu_payload_array, main_origins
```

## Load RSV data
In the below, we compute the scaling distribution from RSV_SMH dataset to be used for scaling the training data. This means that all datasets will be scaled so that their peak values match the distribution of peak values from the RSV_SMH dataset.
For example, if the peak value for a season in the RSV_SMH dataset is 1000, and the peak value for the same season in the NSSP dataset is 100, then the NSSP dataset will be scaled by a factor of 10 to match the RSV_SMH peak.

```{python}
all_datasets_df = pd.read_parquet("RSV_files/RSV_FILLED.parquet")
all_datasets_df = all_datasets_df.rename(columns={'fluseason_week': 'season_week'})
all_datasets_df["week_enddate"] = pd.NaT

season_identifiers = ['datasetH1', 'datasetH2', 'fluseason', 'sample']
time_identifier = 'season_week'

#This sums values across locations for each dataset and week.
location_sums = all_datasets_df.groupby(season_identifiers + [time_identifier])['value'].sum().reset_index()

#This extracts the peak weekly value per season.
season_peaks = location_sums.groupby(season_identifiers)['value'].max().reset_index()
scaling_distribution = season_peaks[season_peaks['datasetH1'] == 'RSV_SMH'].value if 'RSV_SMH' in season_peaks['datasetH1'].unique() else season_peaks.value
```

## RSV configuration

```{r}
n_frames <- arrow::read_parquet("RSV_files/RSV_FILLED.parquet") |>
  group_by(fluseason, datasetH1, sample) |>
  count() |>
  group_by(datasetH1) |>
  summarise(
    n_frames = n(),
    .groups = "drop"
  ) |>
  mutate(
    proportions = c(0.1, 0.1, 0.1, 0.7),
    n_trains = ceiling(n_frames / proportions),
    check = if_else(
      n_trains > n_frames,
      TRUE,
      FALSE
    )
  )
n_frames |> pull(n_trains) |> max()

```


```{python}
# need to build 512 frames per dataset for training
RSV_CONFIG = {
    "100S": {
        "NSSP": {"multiplier": 20},
        "RSV-Net": {"multiplier": 20},
        "NHSN": {"multiplier": 20},
    },
    "30S70M": {
        "NSSP": {"proportion": 0.10, "total": 2229},
        "RSV-Net": {"proportion": 0.10, "total": 2229},
        "NHSN": {"proportion": 0.10, "total": 2229},
        "RSV_SMH": {"proportion": 0.70, "total": 2229},
    },
    "100M": {
        "RSV_SMH": {"multiplier": 1}
    },
}

```


## Build datasets
```{python}
for ds_name, mix_cfg in RSV_CONFIG.items():
    print(f"Building dataset: {ds_name}")
    
    # Build frames using the mixer
    frame_list = dataset_mixer.build_frames(
        all_datasets_df, 
        mix_cfg, 
        season_axis=season_setup, 
        fill_missing_locations="random",
        scaling_distribution=scaling_distribution
    )
    
    # Convert to Xarray
    flu_payload_array, main_origins = build_dataset_from_framelist(frame_list)
    
    # Add metadata
    flu_payload_array = flu_payload_array.assign_attrs(
                main_origins=list(main_origins),
                mix_cfg=mix_cfg.__str__()
    )
    
    # Save to NetCDF
    filename = f"training_datasets/RSV_{ds_name}_{today}.nc"
    flu_payload_array.to_netcdf(filename)
    print(f"Saved {filename}")

```


## Inspect array
```{python}
arr = xr.open_dataarray("training_datasets/RSV_100S_2026-01-16.nc")

all_origin = arr.attrs.get("main_origins", None)
prefixes = [entry.split('/')[0] for entry in all_origin]
segments = []
start = 0
current_prefix = prefixes[0]
for i in range(1, len(prefixes)):
    if prefixes[i] != current_prefix:
        segments.append((start, i - 1, current_prefix))
        start = i
        current_prefix = prefixes[i]
# Add the last segment
segments.append((start, len(prefixes) - 1, current_prefix))
# Output: list of (start_idx, end_idx, prefix)
for seg in segments:
    print(f"{seg[2]}: from index {seg[0]} to {seg[1]} (n={seg[1] - seg[0] + 1})")
```

## Visualize arr
```{python}

# mat = arr.sel(sample=0, feature=0)
# mat.plot()
idx_tp = 0
for i in list(np.arange(idx_tp, idx_tp+5*20, step = 17)):
  print(all_origin[i])

fig, ax = idplots.plot_us_grid(
    data=arr,
    season_axis=season_setup,
    sample_idx=list(np.arange(idx_tp, idx_tp+5*17, step = 17)),
    multi_line=True,
    sharey=False,
)

arr.attrs

```


# TRAINING
The RSV training datasets have been built and saved in the `training_datasets` folder. Each dataset corresponds to a different mixing configuration as specified in the `RSV_CONFIG` dictionary. 

```{python}
import matplotlib.pyplot as plt
import seaborn as sns
from tqdm.auto import tqdm
import torch
from torch import nn
import numpy as np
import pandas as pd
import datetime
import sys
from pathlib import Path
from torch.utils.data import DataLoader
from torch.optim import Adam

# InfluPaint modular imports
from influpaint.utils import SeasonAxis, plotting as idplots
from influpaint.batch.scenarios import get_training_scenario, create_scenario_objects
from influpaint.batch.config import copaint_config_library, create_folders, get_git_revision_short_hash
from influpaint.utils import ground_truth
from influpaint.datasets import loaders as training_datasets
from influpaint.batch.config import transform_library
# CoPaint imports
sys.path.append('CoPaint4influpaint')
from guided_diffusion import O_DDIMSampler

# Configure plotting
sns.set_style("whitegrid")
%matplotlib inline

season_setup = SeasonAxis.for_flusight(remove_us=True, remove_territories=True)
image_size = 64
channels = 1
batch_size=512
epochs=3000
device = "cuda" if torch.cuda.is_available() else "cpu"
print(f"Using device: {device}")

if device == "cuda":
    from influpaint.utils.helpers import cuda_mem_info
    print(cuda_mem_info())
    torch.cuda.empty_cache()
    print(cuda_mem_info())

```


```{python}

scn_id = 868  # Choose your training scenario
experiment_name = "demo_jan2026"  # MLflow experiment name
scenario_spec = get_training_scenario(scn_id)
ddpm, dataset, transform, enrich, scaling_per_channel, data_mean, data_sd = create_scenario_objects(
            scenario_spec, season_setup, image_size, channels, batch_size, epochs, device)

```


```{python}
dataset = training_datasets.FluDataset.from_xarray("training_datasets/RSV_30S70M_2026-01-16.nc",channels=channels,)
scaling_per_channel = np.array(dataset.max_per_feature) # one number per channel 

transforms_spec, transform_enrich = transform_library(
    scaling_per_channel,
    data_mean=dataset.flu_dyn.mean(),
    data_std=dataset.flu_dyn.std(),
)
transform = transforms_spec[scenario_spec.transform_name]
enrich = transform_enrich[scenario_spec.enrich_name]
dataset.add_transform(
    transform=transform["reg"],
    transform_inv=transform["inv"],
    transform_enrich=enrich,
    bypass_test=False,
)

all_samples = np.array([sample.numpy() for sample in dataset]) #dataset is an iterable that yields tensors tranformed
plt.hist(all_samples.flatten());

```


```{python}
dataloader = DataLoader(dataset, batch_size=batch_size, shuffle=True, drop_last=True)
losses = ddpm.train(dataloader, mlflow_logging=True)
```



```{python}
checkpoint_path = f"rsv.pth"
ddpm.write_train_checkpoint(save_path=checkpoint_path)
ddpm.load_model_checkpoint(checkpoint_path)

ddpm.model.eval()
ddpm.model.to(device)

ft_samples = ddpm.sample() # list of size n_diff_step.
ft_samples[0].shape
np.save(f"rsvgen.npy", dataset.apply_transform_inv(ft_samples[-1]))
ft_samples = np.load("rsvgen.npy")
n_show = min(batch_size, 10)

fig, axes = plt.subplots(2, 2, figsize=(2.8 * n_show, 7.5), dpi=100)
for k, loc in enumerate([ 0, 5, 10, 15]):
    ax = axes.flat[k]
    for i in np.arange(3):
        hist_img = dataset.get_sample_raw(i)
        idplots.show_tensor_image(hist_img, ax=ax, place=loc, multi=False) # thicker curve are historical data
        for i in range(n_show):
          gen_img = ft_samples[i]
          idplots.show_tensor_image(gen_img, ax=ax, place=loc, multi=True)
        
    ax.set_title(f"FT gen vs Hist, loc={loc}")
    ax.grid(visible=True, alpha=0.3)
plt.tight_layout()
plt.show()
```